% It was requested by ^^^iulatex^^^ that I follow ProQuest^^^proquest^^^ requirements for the
% abstract, but I have no idea where to find those with the exception of ^^^proquestlength^^^
% limiting the abstract to 775 words.
In this work, we take a look at representation learning.
% In ^^^edit2^^^, Donald Williamson recommended that I should justify the reason for representation
% learning. I added text to do so, but merged it with an explanation of the topic in this one
% sentence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                  %
Representation learning is the field that studies what neural networks learn during the training
process.
%                                                                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To do so, we perform experiments in shape counting in the hopes that the artificial neural network
learns the representation of shapes. The network, at least in part, appears to learn some
representation resembling the shape. We formulate a way to perform shape detection using
prior-research's saliency maps in a novel way, though the algorithm has issues to be addressed at a
later time. Another representation topic that we look at is that of adversarial examples: if a
person wants to reduce the classification performance of a neural network substantially or
completely, there are ways to turn normal images into ``adversarial examples'' without a human
noticing the change. We propose a number of defenses and both analytically and intuitively state
their properties that would, in theory, lead to them performing well. However, the theory did not
pan out in any substantial way, but we make some conjectures as to why this is the case. In all, our
the experiments are semi-successful and we extensively discuss how these topics rely heavily on
representation.